The merger history of primordial-black-hole binaries inferred from GWTC-3

### 2022-09-26 latex/paper.tex
Updates from Overleaf
update

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
in \Fig{posterior-log}.
\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{post-log.pdf}
	\caption{\label{posterior-log}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.45\textwidth]{ratio-log.pdf}
	\caption{\label{ratio-log}
		The ratio of merger rate density from second-merger history
		to that from first-merger history,
		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{m_c, \sigma\}$ in \Eq{log} are fixed to their best-fit values.
	}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{post-power.pdf}
	\caption{\label{posterior-power}
		The marginalized one- and two-dimensional posterior distributions for 
    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.45\textwidth]{ratio-power.pdf}
	\caption{\label{ratio-power}
		The ratio of merger rate density from second-merger history
        to that from first-merger history,
        $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
	}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
% We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
We would also like to thank Xingjiang Zhu, Shen-Shi Du for useful conversations.
This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
the LIGO Scientific Collaboration and the Virgo Collaboration. 
LIGO is funded by the U.S. National Science Foundation. 
Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
with contributions by Polish and Hungarian institutes. 
\end{acknowledgments}

>>>>

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
in \Fig{posterior-log}.
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{post-log.pdf}
	\caption{\label{posterior-log}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{ratio-log.pdf}
	\caption{\label{ratio-log}
		The ratio of merger rate density from second-merger history
		to that from first-merger history,
		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{m_c, \sigma\}$ in \Eq{log} are fixed to their best-fit values.
	}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{post-power.pdf}
	\caption{\label{posterior-power}
		The marginalized one- and two-dimensional posterior distributions for 
    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
	\caption{\label{ratio-power}
		The ratio of merger rate density from second-merger history
        to that from first-merger history,
        $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
	}
\end{figure}

@@

\subsection{Broken Power-law mass function}
We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
\e\label{bpower} 
P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
\q
where $m>M$, and $\al>1$ is the power-law index. The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
Note that $\vth=\{\al, M\}$ and the free parameters are 
$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
\e
\mpbh = M \frac{\al}{\al-1},
\q
\e 
F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
\q

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
	\caption{\label{posterior-bpower}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
	\caption{\label{ratio-bpower}
		The ratio of merger rate density from second-merger history
		to that from first-merger history,
		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
	}
\end{figure}

\subsection{CC mass function}
We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
\e\label{CC} 
P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
\q
where $m>M$, and $\al>1$ is the power-law index. The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
Note that $\vth=\{\al, M\}$ and the free parameters are 
$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
\e
\mpbh = M \frac{\al}{\al-1},
\q
\e 
F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
\q

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
	\caption{\label{post-CC}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
	\caption{\label{ratio-CC}
		The ratio of merger rate density from second-merger history
		to that from first-merger history,
		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
	}
\end{figure}

\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
to the one from first-merger history, namely 
$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
It is clearly that the correction of total merger rate density from 
second-merger history is less than $10\%$.
It is then readily to calculate the ratio of merger rate from 
second-merger history to the one from first-merger history, 
$R_2(t_0)/R_1(t_0) = 0.5\%$.
We therefore conclude that the merger history effect can be safely ignored
when estimating the merger rate (density) of PBHs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
% We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
We would also like to thank Xingjiang Zhu, Xiao-Jin Liu, Shen-Shi Du, and Zhu Yi for useful discussions.
This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
the LIGO Scientific Collaboration and the Virgo Collaboration. 
LIGO is funded by the U.S. National Science Foundation. 
Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
with contributions by Polish and Hungarian institutes. 
\end{acknowledgments}
